### 2008-12-21 talk/ecoop2009/clibackend.tex
add conclusion and future work
add a footnote

At the moment of writing, three backends have been implemented: one for Intel
\emph{x86} processors, one for \emph{PowerPC} processors, and one for the
\emph{CLI Virtual Machine}.  The latter is special because instead of emitting
code for a real CPU it emits code for a virtual machine: before being
executed, the generated code will be compiled again by .NET's own JIT
compiler.

>>>>

At the moment of writing, three backends have been implemented: one for Intel
\emph{x86} processors, one for \emph{PowerPC} processors, and one for the
\emph{CLI Virtual Machine}.  The latter is special because instead of emitting
code for a real CPU it emits code for a virtual machine \footnote{By using the 
\lstinline{Reflection.Emit} namespace and creating \lstinline{DynamicMethod}s.}: 
before being
executed, the generated code will be compiled again by .NET's own JIT
compiler.
